\documentclass{resume} % Use the custom resume.cls style

\usepackage{setspace}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Murtaza Sidhpurwala} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{9029662977 \\ sidhpurwalamurtaza0@gmail.com \\ Mumbai, India} 
\address{\href{https://www.linkedin.com/in/murtaza-sidhpurwala-b89440150/}{Linkedin} \\ \href{https://github.com/murtaza1109}{GitHub}}  %

\begin{document}

\begin{rSection}{Professional Summary}
{C++ Software Engineer with 8 years of experience building high-performance, cross-platform Qt applications. Skilled in multithreading, memory management, UI frameworks (Qt Widgets/QML), and large-scale codebase modernization (Qt5→Qt6).}
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Software Engineer II} \hfill Apr 2023 - Present\\
\textit{Esko Graphics India Pvt. Ltd.} \hfill Bangalore, India
\vspace{-5pt}
\begin{itemize}
\itemsep -3pt
\item \href{https://www.xrite.com/service-support/downloads/i/i1profiler-i1publish_v3_8_5}{i1Profiler} (Color Calibration Software)
\begin{itemize}
\itemsep -3pt
\item Added new Qt-based UI modules and improved calibration workflow for monitor/printer profiles.
\item Migrated 200k+ lines from Qt5 → Qt6 without regressions for cross platform.
\end{itemize}
\item Guided junior engineers on C++, Qt improving team productivity and code maintainability. 
\end{itemize}

\textbf{Engineer} \hfill Sep 2021 - Apr 2023\\
\textit{Einfochips} \hfill Pune, India
\vspace{-5pt}
\begin{itemize}
\itemsep -3pt
\item Built UI from scratch using QML for POC of \textbf{\href{https://www.softacuityinc.com/}{Elsa}} reducing prototype time by 4 weeks.
\end{itemize}

\textbf{Engineer} \hfill Aug 2020 - Sep 2021\\
\textit{Tata Advanced Systems Ltd.} \hfill Mumbai, India
\vspace{-5pt}
\begin{itemize}
\itemsep -3pt
\item Added Qt UI modules for launcher software for \href{https://en.wikipedia.org/wiki/Pinaka_multi-barrel_rocket_launcher}{Pinaka} (Multi Barrel Rocket Launcher).
\end{itemize}

\textbf{Linux Software Developer} \hfill Feb 2020 - Aug 2020\\
\textit{Electropneumatics CNC Controls Pvt. Ltd.} \hfill Mumbai, India
\vspace{-5pt}
\begin{itemize}
\itemsep -3pt
\item Developed Qt-based control systems for \href{https://en.wikipedia.org/wiki/Akash-NG}{Akash-NG}.
\end{itemize}

\textbf{Software Developer} \hfill Jan 2019 - Feb 2020\\
\textit{AM Prototyping Lab Pvt. Ltd.} \hfill Mumbai, India
\vspace{-5pt}
\begin{itemize}
\itemsep -3pt
\item Created UI for Live slicing status, Print queue, Analytics and Fine tuning pages with controller \\ firmware for  \href{https://www.3dware.in/top-down-dlp-3d-printer-cam-machine-9902354.html}{Zeta} DLP 3D printer.
\item Refactored existing codebase for modularity.
\end{itemize}

\textbf{Electronics Engineer} \hfill Oct 2017 - Jan 2019\\
\textit{Zeal Tech.} \hfill Mumbai, India
\vspace{-5pt}
\begin{itemize}
\itemsep -3pt
\item Assisted in developing \href{https://www.zeal-tech.co.in/analytical-instruments.html}{Analytical instruments} such as polarimeters and power supplies in collaboration \\with senior engineers.
\item Designed PCBs for \href{https://www.zeal-tech.co.in/led-marine-lights.html}{Marine LED Lights}.
\end{itemize}

\end{rSection}


\begin{rSection}{Technical SKILLS }
\begin{tabular}{>{\bfseries}  l  @{\hspace{6ex}}l }
 Prog. Languages: & C++11/14/17, Python, Typescript\\
 Frameworks & QT, React, STL, Boost, Catch (Unit Testing ), Next.js, ANT design\\
 Concepts & OOP, Multithreading, SOLID, Design Patterns,Memory Management, RAII \\
 Tools& Git, Visual Studio, CMake, VSCode\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{Education}
{\bf M.H Saboo Siddik college of engineering} \hfill {Mumbai}\\
B.E, Electronics Engineering\hfill {2013-2017}
\end{rSection}

\end{document}